---
output: github_document


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 
## Overview 
The Billboard  R package contains a dataset from the Billboard Hot 100 and a function to generate a table of the top number artists of all time. Users can determine the number they'd like to find with this function. The package contains a dependency on tidyverse in order to clean the top100 dataset. 

## Purpose 
Billboard_100  is an R package that contains datasets of the Billboard Chart Hot 100 acquired from(link), featuring the Hot 100 charts for every week since its first premiere on Monday, Aug. 4, 1958. Finding data on music, artist, and chart numbers can be very daunting and a lot of time spent on Google.  We have made Billboard_100 to keep everything all in one place.  

## Target Audience 
This package was made for anyone who find value in music stats. This package can easily be used for data analysis and provide actionable insights for artists, record labels, or anyone whose interested in the Billboard Hot 100.
 
 
 
 
## Installation 

```{r}
devtools::install_github("aacharya23/billboard100")
```

## Datasets Included 
* top100: A dataset that contains the date, song name, artist, current rank and past rank of the Billboard Hot 100 songs. 

## Function

Functions inside the package:
* TopN_BB100: returns the top ’n’ artist whose made it on the Billboard Hot 100. 

## Basic Usage 

Load billboard100 R package. 

```{r}
library(billboard100)
```

Run the function to generate a table with N number of songs 

```{r}
TopN_BB100(data = BB100, 10)
```



## Package Proposal 
This package will scrape data from the billboard hot 100 website and change depending on the week that the user utilizes the package. Unlike this current phase, the phase III package will not have a dataset that it's working from. Users can perform analyzes of the scraped data similarly to the current package version. 

##
