---
output: github_document


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 
## Overview 
billboard100 contains data from the Billboard Hot 100 dataset that contains all the songs that made this popular music chart since 1958. The functions in the package allow users to analyze the top N songs of all time. The package currently contains dependencies on dplyr.


## Target Audience
This package was made for anyone who find value in music stats. This package can easily be used for data analysis and provide actionable insights for artists, record labels, or anyone who's interested in the Billboard Hot 100.


## Installation 

```{r}
devtools::install_github("aacharya23/billboard100")
```

## Datasets Included 
* top100: A dataset that contains the date, song name, artist, current rank and past rank of the Billboard Hot 100 songs. 

## Function

Functions inside the package:

* top_n: return the top ’n’ artist whose made it on the Billboard Hot 100.
* visualize: visualize the output of top_n as a bar chart

# Description 

#Purpose

#Dependencies/Setup 

#Arguments 


Load billboard100 R package. 

```{r}
library(billboard100)
```

Run the function to generate a table with N number of songs 

```{r}
top_n(data = top100, 10)
```



## Package Proposal 
This package will scrape data from the billboard hot 100 website and change depending on the week that the user utilizes the package. Unlike this current phase, the phase III package will not have a dataset that it's working from. Users can perform analyzes of the scraped data similarly to the current package version. Additionally, we will add functionalities like being able to create visualizations of the data and pull charts of data from certain years only. 

##
