---
output: github_document


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 
## Overview 

This package was made for anyone who find value in music stats. This package can easily be used for data analysis and provide actionable insights for artists, record labels, or anyone whose interested in the Billboard Hot 100.
 
 
 
 
## Installation 

```{r}
devtools::install_github("aacharya23/billboard100")
```

## Datasets Included 
* top100: A dataset that contains the date, song name, artist, current rank and past rank of the Billboard Hot 100 songs. 

## Function

Functions inside the package:
* TopN_BB100: returns the top ’n’ artist whose made it on the Billboard Hot 100. 


Load billboard100 R package. 

```{r}
library(billboard100)
```

Run the function to generate a table with N number of songs 

```{r}
TopN_BB100(data = BB100, 10)
```



## Package Proposal 
This package will scrape data from the billboard hot 100 website and change depending on the week that the user utilizes the package. Unlike this current phase, the phase III package will not have a dataset that it's working from. Users can perform analyzes of the scraped data similarly to the current package version. 

##
